### 2020-06-05 Report/aws_325ghz_study.tex
added few tables and figures for QRNN, but no text

\section{Cloud correction by QRNN}
%
There are two main drawbacks of the simple scheme introdoced in the previous
section. The filtering/correction only involves a single 325\,GHz channel. The
scheme could be extended to consider a higher number of channels, but there is
no obvious formulation of the expressions to apply. The second problem is that
no case-specific uncertainty estimate is provided, only the overal bias and
standard deviations are known. The first drawback hints towards using a machine
learning approach, and the second one suggests to use the special form denoted
QRNN (Quantile Regression Neural Network), that was introduced for ratmospheric
retrievals by \citet{pfreundschuh:aneur:18}.

@@

\section{Discussion}

>>>>

\section{Cloud correction by QRNN}
%
There are two main drawbacks of the simple scheme introduced in the previous
section. The filtering/correction only involves a single 325\,GHz channel. The
scheme could be extended to consider a higher number of channels, but there is
no obvious formulation of the expressions to apply. The second problem is that
no case-specific uncertainty estimate is provided, only the overal bias and
standard deviations are known. The first drawback hints towards using a machine
learning approach, and the second one suggests to use the special form denoted
QRNN (Quantile Regression Neural Network), that was introduced for atmospheric
retrievals by \citet{pfreundschuh:aneur:18}.

@@

\subsection{QRNN model}
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss_median.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss_median}
\end{figure}

\subsection{Prediction accuracy}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C33}
	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C35}
	\includegraphics[height=60mm]{distribution_predicted_C36}
	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
	\label{fig:pdf:qrnn}
\end{figure}

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{Channel_C34.png}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
		simulations before and after correction with QRNNs. Predictions from both three channel and four channel options for 325 GHz are shown. }
	\label{fig:qrnn_C34:deviations}
\end{figure}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     & -0.006 & 0.634 &              0.008 &      - \\
uncorrected               & -0.678 & 3.678 &            -10.320 &     - \\
corrected (three channel) &  0.050 & 0.617 &             -0.506 &      2.730 \\
corrected (four channel)  &  0.077 & 0.608 &             -0.446 &      2.957 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     &  0.004 & 0.455 &              0.006 &      - \\
uncorrected               & -1.341 & 5.905 &             -7.482 &      - \\
corrected (three channel) & -0.065 & 0.820 &             -2.312 &      4.902 \\
corrected (four channel)  & -0.003 & 0.821 &             -2.158 &      4.906 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     &  0.002 & 0.451 &             -0.017 &     - \\
uncorrected               & -0.981 & 4.706 &             -8.755 &     - \\
corrected (three channel) &  0.048 & 0.578 &             -0.596 &      4.189 \\
corrected (four channel)  &  0.044 & 0.573 &             -0.603 &      4.280 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
	\label{tab:qrnn:C33}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.626 &             -0.003 &      - \\
uncorrected                & -0.428 & 2.661 &            -12.451 &      - \\
corrected (three channel)  &  0.036 & 0.601 &             -0.202 &      1.451 \\
corrected (four channel)   &  0.017 & 0.572 &             -0.279 &      1.781 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
	\label{tab:qrnn:C35}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                     & -0.000 & 0.888 &              0.005 &      - \\
uncorrected               & -0.269 & 2.059 &            -11.899 &      - \\
corrected (three channel) &  0.053 & 0.797 &             -0.143 &      1.263 \\
corrected (four channel)  &  0.033 & 0.763 &             -0.140 &      1.148 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
	\label{tab:qrnn:C36}
\end{table}

\subsection{Uncertainity estimation}
\section{Discussion}
